Efficiently stable presentations from error-correcting codes

### 2025-09-29 daj-revision2/referee-response.txt

3. page 10, Lemma 2.5: δ sould be √δ. The fact that you do not put paren-
theses is misleading, it could be understood as (Pr
i=1 ∥...∥τ ) + 2δ. Put
parentheses in the sum, or write (r + 1)√δ + P|r|
i=1 ∥...∥τ .

A: Corrected

4. page 12, (7): μS is not a probability measure.

A: This was a typo; we had meant to include the scaling with |r| as in your previous report.

@@

6. page 20, line 6: the phrasing “to guarantee that Ri is independent of the
order...” is misleading. Probably what you mean it that the presentation
(20) defines the same group, whatever the order in which the xi are mul-
tiplied. But as a relation, the order always matters, even after adding the
relations R′
ijj′ . For example, the notion of (ε, μ)-almost homomorphism
changes is the order changes.

A: Right, we corrected this

7. This is really unimportant, but I meant that the two groups in the state-
ment of the lemma are only isomorphic, and I kind of agreed that the two
groups in the proofs were equal.

A: [T: He is referring to Lemma 3.1. I don't really get it. We should say that Z_2^k and the presentation are isomorphic, not equal? Then we need to update this all over. Michael?]

8. page 20, Definition 3.3 and above. You write “we state the definition for
the case of a general prime power q” but then there is no q, just 2. So
both occurancies of 2 should be replaced by q.

A: Right, corrected

9. page 22, line 1-2: you should write down the assumption you have on d
(for d ≥ q, the dimension you write is clearly incorrect).

A: added

10. page 24, line 8. You could say more clearly that you fix ti one and for all,
and that the way they are chosen has no impact on the statements (it was
not clear to me whether they are allowed to change or not, and how they
are chosen).

A: Yes, added

11. page 24, line 3 after Figure 3: is the formula for M correct? I count
qm ×m×q ×q +qm ×2t ×2t = (m+1)qm+2, so either I did not understand
what the tester implied by the figure means, or there is a typo.

A: You are right, this hadn't been updated from an earlier change. We fixed it.

@@

12. page 24, line -7: k = t(d + 1)m?

A: [T: This is what we write, what is the question?]

13. page 25, Theorem 4.1. There is a typo in the formula for δ(ε) (your
formula gives δ(ε) ≥ C; this form of the theorem is of course true, but not
very impressive).

A: Yes, the brackets had been closed in the wrong way in the latex; thanks.

@@

14. page 25, line 1 in the proof of Theorem 4.1: μS = μR.

A: Corrected

15. page 25, Claim 4.2: do you need Claim 4.2? Corollary 2.15 that you use
later does not require that ϕ takes its values in the hermitian unitaries.

A: You're right, these relations are supserseded by the "Hadamard" relations and were not necessary. We removed them from the presentation, removed Claim 4.2, and adapted the rest of the text.

16. page 26, Claim 4.4: why the √ε? Claim 4.3 exactly says that ϕ is
(δ, μS )-close to U with δ = O(ε), and Lemma 2.7 (or its proof) says that
E∥[Uu,α, Uv,α′ ] − [ϕ(su,α), ϕ(sv,α′ )]∥2 ≤ 16δ for any probability measure
on pairs whose marginals are μS .

Yes this was a typo in the last line of the proof, we corrected it.

17. page 28, line 3: what you write is not true for a fixed u, but it is true on
average over u.

A: Corrected

18. page 29, line -5– -1: the conventions for the notation poly here (given
in footnote 7) do not match those of [JNV+22]. For example, on the
last line of page 23 of [JNV+22], you have an expression of the form
poly(ε, n−1) + e−Ω(r/m2) that becomes, in the conclusion of [JNV+22,
Theorem 4.1] poly(ε, n−1, e−Ω(r/m2)). And similarly all over [JNV+22].
So, the way you prove Theorem 4.1 has two problems: (a) you do not
prove that the presentation given in (22) is stable in the sense of Definition
1.2 (because you do not prove limε δ(ε) = 0) and (2) your convention of
poly contradicts your use of it.
When you write Yes, we are sure that the modulus goes to 0 with epsilon,
I agree that this is true, but where is it proven? I did not find the proof
written, neither in [JNV+22] nor in your submission. I thought that what
is proven in [JNV+22] is with δ(ε) ≤ C(mC + dC )(ε1/C + q−1/C ) for some
universal C, which is C(mC + dC )q−1/C > 0 for ε = 0.
If you want to stick to the convention that limε δ(ε) = 0, one cheap way is
to exploit Lemma 2.6 and [GH17] to explain that the modulus of stabil-
ity in Theorem 4.1 is something like min(C1ε, C2poly(ε, 1/q)) for a good
(=polynomial in the parameters) constant C2 and a bad (=exponential in
the parameters) constant C1.
19. page 29, line -2: in [JNV+22], there is an assumption r ≥ 12mt (which
in the notation here becomes r ≥ 12m(d + 1)). Do you have assumptions
that ensure that Ω(tm2) satisfies this inequality?
20. page 29, line -1: you could explain why the existence of Gc implies the
conclusion of the theorem: write the homomorphism that is δ(ε)-close to
ϕ.
21. Here is what I had in mind in my comment 35.
Lemma 1. Assume that G = ⟨S, R⟩ is (δ, μR, μS )-stable, and let νR be
another probability measure on R such that νS = μS .1 Then every (ε, μR)-
almost representation is a (CEr∼ν |r|2δ(ε), νR)-almost representation.2
Proof. By the definition of stability, an (ε, μR)-representation is (δ(ε), μS )-
close to a representation, that is (δ(ε), νS )-close to a representation (νS =
νR). Lemma 2.7 implies that it is a (Cδ(ε), νR)-almost representation.
Let us deduce the new inequality in Corollary 2.8:
∀ε ≤ 1
k − 1 , δk(ε) ≥ kε
C′ .
Let G = ([k], E) be a perfect matching on k vertices, consider νR the
uniform probability measure on {[xi, xi] | ij ∈ E}. Then νS = μS is the
uniform probability measure {x1, . . . , xk}.
1We use the notation from your remark 2.8.
2C is the universal constant in your Lemma 2.7.
3
Consider A the map from Claim 4.2. It is a ( 1
k−1 , μR)-almost represen-
tation. So Φ : xi 7 → (Ai, 1) is a (ε, μR)-almost representation if M ⊕ C
is equipped with the trace τ ε(x, λ) = (k − 1)ετ M(x) + (1 − (k − 1)ε)λ.
Moreover, for every edge ij, ∥[Φ(xi), Φ(xj )] − 1∥2
τ ε = 2(k − 1)ε, and the
lemma implies
2(k − 1)ε = 1
|E|
X
ij∈E
∥[Ai, Aj ] − 1∥2
τ ε ≤ C16δk(ε)

### 2025-09-29 daj-revision2/efficient_stability.tex
more referee edits

\begin{lemma}\label{lem:g-phi}
Let $G=\langle S:R\rangle$ and $\mu_S$ a distribution on $S$.  Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ and $g:G\to \mathcal{U}(\mN)$ a representation such that $g$ is $(\delta,\mu_S)$ close to $\phi$. Then for any $r\in\mathcal{F}(S)$, it holds that 
\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau + 2\delta\;,\]
where $r_i$ denotes the $i$-the element of $r$ (which is an element of $S\cup S^{-1}$).
\end{lemma}

\begin{proof}
  Let $r$ be a word in the elements of $S$ and their inverses. For $0\leq i \leq |r|$ we write $r_{\leq i}$ for the length-$i$ prefix of $r$ (which is $1_G$ if $i=0$), and $r_{> i}$ for its length-$(|r|-i)$ suffix (which is $1_G$ if $i=|r|$). 
  Using the triangle inequality, 
  \begin{align*}  
    \|\phi(r)-w^*g(r)w\|_\tau &\leq \sum_{i=1}^{|r|} \| w^*{g}(r_{\leq i}) w{\phi}(r_{>i})-w^* {g}(r_{<i})w\phi(r_{\geq i}))\|_\tau  + \|(w^*w-I_\cM)\phi(r)\|_\tau \\
    &\leq \sum_{i=1}^{|r|} \| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} + \|w^*w-I_\cM\|_\tau \\ 
    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
    \end{align*}
    Here, for the last inequality we used that $g(r_i)$, $\phi(r_i)$ are unitaries, and $w$ an isometry, so either of them contracts the norm.  
\end{proof}

@@

Using the definition of $\phi$, followed by the triangle inequality, 
\begin{align*}
\|\phi(r)-I\|_\tau &= \|\phi'(w(r))-I\|_\tau\\
&= \|\phi'( u_1 (r'_{1})^{\eps'_1}u_1^* \cdots u_L (r'_{L})^{\eps'_L} u_L^* ) - I \|_\tau\\
&\leq  \sum_{j=1}^L \|\phi'( u_j (r'_{j})^{\eps'_j}u_j^* ) - I \|_\tau\\
&=  \sum_{j=1}^L \|\phi'( r'_{j}) - I \|_\tau\\
&\leq L \max_{r'\in R'} \|\phi'(r')-1\|_\tau\;.
\end{align*}
%Let $S''=S\cup S'$ and $R''=R\cup R'$. Let $\mu_R''$ be the equal mixture of $\mu_R$ and $\mu_{R'}$.
 From the above it follows that $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$ where 
\[\eps' \leq  L \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.\]
%In particular, $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$. 
%Note that because $G=\langle S:R\rangle$ is stable, then $G=\langle S'':R''\rangle$ is also stable. This is
Applying the assumption, $\phi$ is $(\delta(\eps'),\mu_S)$-close to a unitary representation $g$ of $G$ on some $(\mathcal{N}, \tau^\mN)\in \mC$. 
For $s'\in S'$, write $s' = w'$ where $w'\in\mathcal{F}(S)$ is a word in the generators from $S$ and their inverses. Further replacing each generator $s_i$ from $S$ by the word $w_i$ identified at the start of the proof gives $s'=w''$ where $w''\in \mathcal{F}(S')$ is a product of the $w_i$ and their inverses.

Using the same reasoning as in the first part, it follows that 
\begin{equation}\label{eq:sg-1}
   \|\phi'(w''(s')^{-1})-I\|_\tau \leq LL' \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
\end{equation}
where $L'=\Delta(DD')$ with $D=\max_{s'\in S'}|w'|$ and $\Delta$ the Dehn function of $\langle S:R\rangle$.
 But $\phi'(w''(s')^{-1}) = \phi'(w'')\phi'((s')^{-1})=\phi(w')\phi'(s')^{-1}$. Using Lemma~\ref{lem:g-phi} we deduce that 
\begin{align}
 \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + 2\eps'\notag\\
 &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1} + 2\eps'\;.\label{eq:sg-2}
\end{align}
It follows from~\eqref{eq:sg-1} and~\eqref{eq:sg-2} that $\phi'$ is $\delta'(\eps)$-close to $g$, where 
\begin{align*}
\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1}  + 2\eps'  +  LL' \eps (\min_{r'}\mu_R'(r'))^{-1}\\
&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
\;.
%\\
%&\leq \big(LL' (\min_{s\in S} \mu(s))^{-1}(\min_{r'}\mu_R'(r'))^{-1}\big) \eps\;.
\end{align*}
\end{proof}

@@

\begin{lemma}\label{lem:l1}
  Let $G=\langle S:R\rangle$ be a finite presentation, and $\mu_R$ a distribution on $R$. For a relation $r\in R$, let $|r|$ denote its length as a word in $\mathcal{F}(S)$. Define the following measure on $S$
  \begin{equation}\label{eq:mus}
     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} \mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
  \end{equation}
  where $\delta_{r_i}$ assigns probability $1$ to the $i$-th element of $r$, or its inverse, depending which lies in $S$. Then for any tracial von Neumann algebra $(\cM,\tau)$ and homomorphism $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$, if $\phi$ is $(\delta,\mu_S)$ close to a representation of $G$ then $\phi$ is also an $(O(\delta),\mu_R)$-almost homomorphism. (Here the constant implicit in the $O(\cdot)$ depends linearly on $\Es{r\sim \mu_R}|r|^2$.)
  \end{lemma}

  \begin{proof}
    Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ be as in the lemma, and let $g$ be a $(\delta,\mu_S)$ close representation of $G$.
   Using the triangle inequality and $g(r)=1_\mN$ and then Lemma~\ref{lem:g-phi}, 
  \begin{align*}
  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau &\leq \Es{r\sim \mu_R}\|\phi(r)-w^*g(r)w\|_\tau + \|w^*w-I_\mM\|_\tau\\
  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|w^*w-I_\mM\|_\tau +2\delta \\
  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} \| w^* g(r_i)w -\phi(r_i)\|_\tau +   \|w^*w-I_\mM\|_\tau +2\delta\\
  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S } \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
  &\leq 8\delta \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\;,
  \end{align*}
  where 
	%the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and 
	for the last line we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
  \end{proof}

@@

For the remainder of this section we specialize the discussion to the case where $q=2$. 
We make the simple but key observation that a parity check matrix for a code of dimension $k$ implies a finite group presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e\;, \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$, already introduced in~\eqref{eq:gh-intro} and which with the present notation reads
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose \emph{all} pairwise commutation relations, as in~\eqref{eq:wtgh-intro}, then we obtain the following.

@@

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_2$ linear code and $r\in \N$.
An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F_2^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
\end{definition}

@@

We introduce a family of codes that will lead to interesting presentations $G(h)$, whose stability we are able to analyze.
Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$. It follows that the linear span of all $(f(x))_{x\in \F_q^m}$, when ranging over all possible $\{c_\alpha\}$, defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.

@@

We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$. The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}. %From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$. 
The description makes use of interpolation coefficients, which are defined as follows. Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
 \begin{equation}\label{eq:interp-coeff}
 \alpha_{u,v,i} = \prod_{\substack{i'=0\\i'\neq i}}^{d}  \frac{v - (u + t_{i'})}{t_i - t_{i'}}~.
 \end{equation}
These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
%\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
that for all $v \in \F_q$, 
\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]

@@

This notation is used in Figure~\ref{fig:bRM-tester}, in which we give an algorithmic description of the natural local tester associated with $\code_{\bRM}$. This tester is obtained by composing, following the template described in Section~\ref{sec:code-comp}, the local tester for the Reed-Muller code over $\F_q$ described in Figure~\ref{fig:RM-tester} with the local tester for the Hadamard code.
Let $(h_\bRM,\nu)$ be the tester that is implied by the figure. Then $h_\bRM\in \F_2^{M\times N}$, where $N=q^{m+1}$ and $M=mq^m\cdot q^{m+2}$, and $\nu$ is the distribution on $[M]$ implied by the description.

@@

The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn.% each time using a set of relations to evidence a particular structure among these unitaries. Eventually, this will allow us to define the required families of projective measurements from them. 
We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.

>>>>

\begin{lemma}\label{lem:g-phi}
Let $G=\langle S:R\rangle$ and $\mu_S$ a distribution on $S$.  Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ and $g:G\to \mathcal{U}(\mN)$ a representation such that $g$ is $(\delta,\mu_S)$ close to $\phi$. Then for any $r\in\mathcal{F}(S)$, it holds that 
\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, (|r|+1)\sqrt{\delta} + \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau\;,\]
where $r_i$ denotes the $i$-the element of $r$ (which is an element of $S\cup S^{-1}$).
\end{lemma}

\begin{proof}
  Let $r$ be a word in the elements of $S$ and their inverses. For $0\leq i \leq |r|$ we write $r_{\leq i}$ for the length-$i$ prefix of $r$ (which is $1_G$ if $i=0$), and $r_{> i}$ for its length-$(|r|-i)$ suffix (which is $1_G$ if $i=|r|$). 
  Using the triangle inequality, 
  \begin{align*}  
    \|\phi(r)-w^*g(r)w\|_\tau &\leq \sum_{i=1}^{|r|} \| w^*{g}(r_{\leq i}) w{\phi}(r_{>i})-w^* {g}(r_{<i})w\phi(r_{\geq i}))\|_\tau  + \|(w^*w-I_\cM)\phi(r)\|_\tau \\
    &\leq \sum_{i=1}^{|r|} \Big(\| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} \Big)+ \|w^*w-I_\cM\|_\tau \\ 
    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + |r|\|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
    \end{align*}
    Here, for the last inequality we used that $g(r_i)$, $\phi(r_i)$ are unitaries, and $w$ an isometry, so either of them contracts the norm.  
\end{proof}

@@

Using the definition of $\phi$, followed by the triangle inequality, 
\begin{align*}
\|\phi(r)-I\|_\tau &= \|\phi'(w(r))-I\|_\tau\\
&= \|\phi'( u_1 (r'_{1})^{\eps'_1}u_1^* \cdots u_L (r'_{L})^{\eps'_L} u_L^* ) - I \|_\tau\\
&\leq  \sum_{j=1}^L \|\phi'( u_j (r'_{j})^{\eps'_j}u_j^* ) - I \|_\tau\\
&=  \sum_{j=1}^L \|\phi'( r'_{j}) - I \|_\tau\\
&\leq L \max_{r'\in R'} \|\phi'(r')-1\|_\tau\;.
\end{align*}
%Let $S''=S\cup S'$ and $R''=R\cup R'$. Let $\mu_R''$ be the equal mixture of $\mu_R$ and $\mu_{R'}$.
 From the above it follows that $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$ where 
\begin{equation}\label{eq:sg-1a}
\eps' \leq  L^2 \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.
\end{equation}
%In particular, $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$. 
%Note that because $G=\langle S:R\rangle$ is stable, then $G=\langle S'':R''\rangle$ is also stable. This is
Applying the assumption, $\phi$ is $(\delta(\eps'),\mu_S)$-close to a unitary representation $g$ of $G$ on some $(\mathcal{N}, \tau^\mN)\in \mC$. 
For $s'\in S'$, write $s' = w'$ where $w'\in\mathcal{F}(S)$ is a word in the generators from $S$ and their inverses. Further replacing each generator $s_i$ from $S$ by the word $w_i$ identified at the start of the proof gives $s'=w''$ where $w''\in \mathcal{F}(S')$ is a product of the $w_i$ and their inverses.

Using the same reasoning as in the first part, it follows that 
\begin{equation}\label{eq:sg-1}
   \|\phi'(w''(s')^{-1})-I\|_\tau \leq (LL')^2 \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
\end{equation}
where $L'=\Delta(DD')$ with $D=\max_{s'\in S'}|w'|$ and $\Delta$ the Dehn function of $\langle S:R\rangle$.
 But $\phi'(w''(s')^{-1}) = \phi'(w'')\phi'((s')^{-1})=\phi(w')\phi'(s')^{-1}$. Using Lemma~\ref{lem:g-phi} we deduce that 
\begin{align}
 \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + (|w'|+1)\sqrt{\eps'}\notag\\
 &\leq \delta(\eps')^{1/2}  (\min_{s\in S} \mu(s))^{-1} + (|w'|+1)\sqrt{\eps'}\;.\label{eq:sg-2}
\end{align}
It follows from~\eqref{eq:sg-1},~\eqref{eq:sg-2} and~\eqref{eq:sg-1a} that $\phi'$ is $\delta'(\eps)$-close to $g$, where $\delta'(\eps)$ scales as claimed in the lemma. 
%\begin{align*}
%\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-2}  + (L')^2 \eps'  +  (LL')^2 \eps (\min_{r'}\mu_R'(r'))^{-2}\\
%&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
%\;.
%\\
%&\leq \big(LL' (\min_{s\in S} \mu(s))^{-1}(\min_{r'}\mu_R'(r'))^{-1}\big) \eps\;.
%\end{align*}
\end{proof}

@@

\begin{lemma}\label{lem:l1}
  Let $G=\langle S:R\rangle$ be a finite presentation, and $\mu_R$ a distribution on $R$. For a relation $r\in R$, let $|r|$ denote its length as a word in $\mathcal{F}(S)$. Let $\mu_S$ be the probability measure on $S$ defined by
  \begin{equation}\label{eq:mus}
     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} |r|\mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
  \end{equation}
  where $\delta_{r_i}$ assigns probability $1$ to the $i$-th element of $r$, or its inverse, depending which lies in $S$. Then for any tracial von Neumann algebra $(\cM,\tau)$ and homomorphism $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$, if $\phi$ is $(\delta,\mu_S)$ close to a representation of $G$ then $\phi$ is also an $(O(\delta),\mu_R)$-almost homomorphism. (Here the constant implicit in the $O(\cdot)$ depends linearly on $\Es{r\sim \mu_R}|r|^2$.)
  \end{lemma}

  \begin{proof}
    Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ be as in the lemma, and let $g$ be a $(\delta,\mu_S)$ close representation of $G$.
   Using the triangle inequality and $g(r)=1_\mN$ and then Lemma~\ref{lem:g-phi}, 
  \begin{align*}
  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau^2 &\leq \Es{r\sim \mu_R} 2\|\phi(r)-w^*g(r)w\|^2_\tau + 2\|w^*w-I_\mM\|^2_\tau\\
  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}4|r|\| w^* g(r_i)w -\phi(r_i)\|_\tau^2 + O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} 4|r|\| w^* g(r_i)w -\phi(r_i)\|_\tau^2 +  O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
  &\leq 4\Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S } \| w^* g(s)w -\phi(s)\|_\tau^2 +   O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
  &=  O\Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\delta\;,
  \end{align*}
  where 
	%the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and 
	for we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
  \end{proof}

@@

For the remainder of this section we specialize the discussion to the case where $q=2$. 
We make the simple but key observation that a parity check matrix for a code of dimension $k$ implies a finite group presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e\;, \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that the choice of order in which the $x_j$ are multiplied in $R_i$ will not affect the resulting group, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$, already introduced in~\eqref{eq:gh-intro} and which with the present notation reads
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose \emph{all} pairwise commutation relations, as in~\eqref{eq:wtgh-intro}, then we obtain the following.

@@

\begin{definition}[$r$-local linear tester]\label{def:code-test}
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F_q^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
\end{definition}

@@

We introduce a family of codes that will lead to interesting presentations $G(h)$, whose stability we are able to analyze.
Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$. \tnote{added:}Let $1\leq d < q$. Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
\[
	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
\]
where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$. It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$. It follows that the linear span of all $(f(x))_{x\in \F_q^m}$, when ranging over all possible $\{c_\alpha\}$, defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.

@@

We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$. The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}. %From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$. 
The description makes use of interpolation coefficients, which are defined as follows. Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. \tnote{adding:}(These are fixed once and for all, and their choice does not impact any subsequent statement.) Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
 \begin{equation}\label{eq:interp-coeff}
 \alpha_{u,v,i} = \prod_{\substack{i'=0\\i'\neq i}}^{d}  \frac{v - (u + t_{i'})}{t_i - t_{i'}}~.
 \end{equation}
These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
%\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
that for all $v \in \F_q$, 
\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]

@@

This notation is used in Figure~\ref{fig:bRM-tester}, in which we give an algorithmic description of the natural local tester associated with $\code_{\bRM}$. This tester is obtained by composing, following the template described in Section~\ref{sec:code-comp}, the local tester for the Reed-Muller code over $\F_q$ described in Figure~\ref{fig:RM-tester} with the local tester for the Hadamard code.
Let $(h_\bRM,\nu)$ be the tester that is implied by the figure. Then $h_\bRM\in \F_2^{M\times N}$, where $N=q^{m+1}$ and $M=q^m\cdot m \cdot q \cdot q +  q^{m}\cdot q \cdot q = (m+1)q^{m+2}$, and $\nu$ is the distribution on $[M]$ implied by the description.

@@

The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn.% each time using a set of relations to evidence a particular structure among these unitaries. Eventually, this will allow us to define the required families of projective measurements from them. 
%We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
